### 2023-02-22 paper/main.tex
main.tex

\documentclass[a4paper]{revtex4-2}
\usepackage[margin=0.75in, top=1.05in, left=0.85in]{geometry}
\usepackage[italian]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

\makeatletter
\let\it@comma@def\active@comma
\makeatother

\begin{document}
\title{}
\author{Mattia Sotgia}
\affiliation{Università degli Studi di Genova, Dipartimento di Fisica}
\date{\today}
\begin{abstract}
\end{abstract}

\maketitle

\section{Introduzione}

\end{document}